Short_note_captured_phenotype

### 2024-12-11 Short_note_captured_phenotype_journal_version.qmd
Corrections supplementary graphs

@@

ggplot(data = OBSMER_Bycatch_BL_PHO, aes(BODY_MASS, MESH_SIZE, color = TARGETED_ISSCAAP)) + geom_jitter()
# For the interpretation of the latter effect: a large majority of large mesh size (>200mm) are associated with targeting miscellaneous demersal fishes (i.e. mainly mofishes or Zeidae)

>>>>

ggplot(data = Decl_Obs_Merged_Bycatch_BM_DCO, aes(BODY_MASS, MESH_SIZE, color=TARGETED_ISSCAAP)) + geom_jitter()
# For the interpretation of the latter effect: a large majority of large mesh size (>200mm) are associated with targeting miscellaneous demersal fishes (i.e. mainly mofishes or Zeidae)

@@

ggplot(data = OBSMER_Bycatch_BL_PHO, aes(BODY_LENGTH, MESH_SIZE, color = TARGETED_ISSCAAP)) + geom_jitter()
# For the interpretation of the latter effect: a large majority of large mesh size (>200mm) are associated with targeting miscellaneous demersal fishes (i.e. mainly mofishes or Zeidae)
